\documentclass[letterpaper,12pt]{article}
%\documentclass[letterpaper,12pt,answers]{exam}
\usepackage{txfonts,multicol, fullpage}
\usepackage{graphicx}
%\usepackage{../../../../std}
%\setlength{\voffset}{-0.5 in}
%\setlength{\hoffset}{-0.5 in}
%\setlength{\textwidth}{7.9 in}
%setlength{\oddsidemargin}{-0.8cm}
\setlength{\textheight}{10.5 in}
\setlength{\topmargin}{-1 in}
\setlength{\columnsep}{30pt}
\setlength{\headsep}{18pt}
\setlength{\parindent}{5pt}
\setlength{\parskip}{12pt}
%\setlength{\columnseprule}{1pt}
\DeclareGraphicsExtensions{.pdf, .eps, .jpg}

\raggedbottom
\renewcommand{\baselinestretch}{1}
\lefthyphenmin=4
\righthyphenmin=4

%\newcommand{\mb}{\mathbf}
%\newcommand{\qed}{\hfill$\Box$}
%\newcommand{\sol}{\item[]{\it Solution}:  }
%\newcommand{\ds}{\displaystyle}
%\renewcommand{\span}{\textrm{span}}
%\newcommand{\rref}{\textrm{rref}}
%\newcommand{\R}{\mathbb{R}}

\newcommand{\goes}{\rightarrow}
\newcommand{\mb}{\mathbf}
\newcommand{\qed}{\hfill$\Box$}
\newcommand{\sol}{\item[]{\it Solution}:  }
\newcommand{\ds}{\displaystyle}
\renewcommand{\span}{\textrm{span}}
\newcommand{\rref}{\textrm{rref}}
\newcommand{\R}{\mathbb{R}}
\newcommand{\rank}{\textrm{rank}}
\newcommand{\nullity}{\textrm{null}}
\renewcommand{\ker}{\textrm{ker}}
\newcommand{\im}{\textrm{im}}
\newcommand{\Z}{\mathbb{Z}}
\newcommand{\Q}{\mathbb{Q}}



\raggedbottom
\begin{document}
\centerline{}
\rightline{\large \bf Chapter 7.2 Worksheet \qquad\qquad\qquad Name \underline{\qquad\qquad\qquad\qquad\qquad}}\medskip
%\pagestyle{headandfoot}

\noindent \begin{tabular}{llc}
 & {\bf Objectives} & Rate your understanding of the objective \\ \hline

Objective 1 & Understand how to find a volume by &1\qquad 2\qquad 3 \qquad 4 \qquad 5 \\ & integrating the area of a cross section. &\\
Objective 2 & Calculate solids of revolution with the &1\qquad 2\qquad 3 \qquad 4 \qquad 5 \\ & washer method. &\\
Objective 3 & Calculate solids of revolution with the &1\qquad 2\qquad 3 \qquad 4 \qquad 5 \\ & disk method. & \\ \hline
\end{tabular}

\bigskip\bigskip

\centerline{\bf \large Warmup}
\noindent Evaluate the folowing integrals. (By yourself)
\begin{enumerate}\begin{multicols}{3}
\item $\ds \int e^{x}\sin(x) dx$
\item $\ds \int -\frac{\ln(x)}{x^2} dx$
\item $\ds \int _{2}^{3} -\frac{\sin(\ln(x))}{x} dx$
\end{multicols}
\end{enumerate}

\centerline{\bf \large Problems}
\noindent These problems involve the disk method. You may reference Example 205 in your example packet. (In groups)
\begin{enumerate}
\item Find the volume of a right cylinder with a radius of 5 and height of 10 using the disk method. 
\item Find the volume, of the cone from the last problem, that is less than 5 units above the base of the cone.
\item Find the volume of a solid formed by revolving the curve $ x = \sin(y) + y $ around the y-axis, bounded by $ y = 0 $ and $ y = 2\pi $.

\end{enumerate}

\noindent These problems involve the washer method. You may reference Example 207 in your example packet. (In groups)
\begin{enumerate}
\item Given that the solid in the last problem was actually hollow, and had an inner wall defined by revolving the curve $ x = \sin(y) + 0.5\cdot y $, find its volume.
\item Consider the region between the curves $ y = x^2 $ and $\ds y = \frac{x^2}{4} + 3 $. Find the volume of the solid formed by revolving this region about the x-axis.

\end{enumerate}

\centerline{\bf \large Self Quiz}
\centerline{(By yourself)}
\begin{enumerate}
\item Find the general formula for the volume of a cone by writing and evaluating an integral using the disk method. The formula should be in terms of $r$, the radius of the cone at its base, and $h$, the height of the cone.
\item Find the general formula for the volume of a square pyramid by writing and evaluating an integral. The formula should be in terms of $s$, the side length of the base, and $h$.
\end{enumerate}


\vskip 2 in

\centerline{\large \bf Reflection}
% this can be copied from the top of the worksheet
\noindent \begin{tabular}{llc}
 & {\bf Objectives} & Rate your understanding of the objective \\ \hline

Objective 1 & Understand how to find a volume by &1\qquad 2\qquad 3 \qquad 4 \qquad 5 \\ & integrating the area of a cross section. &\\
Objective 2 & Calculate solids of revolution with the &1\qquad 2\qquad 3 \qquad 4 \qquad 5 \\ & washer method. &\\
Objective 3 & Calculate solids of revolution with the &1\qquad 2\qquad 3 \qquad 4 \qquad 5 \\ & disk method. & \\ \hline
\end{tabular}
\bigskip

\noindent
Study Skills:
	\begin{itemize}
		\item Remember to read through examples from the book BEFORE your professor goes over the section in class.
		\item After class read through the examples in your notes from that day and try to do the problems yourself (without looking at your notes).
		\item After class read through the examples from the book in the section you JUST covered and make sure you understand them.
	\end{itemize}



\end{document}


